Kid tangrams joint analysis

### 2025-11-14 code/ms_analysis.Rmd
examples for expt 3, latex adventures

ggplot(joint_demog, aes(x = trial + 1, y = all_words, color = type)) +
  geom_jitter(alpha = .5, color = "grey") +
  stat_summary(fun.data = "mean_cl_boot") +
  scale_x_continuous(breaks = seq(1, 20, 1), expand = c(0, 0)) +
  scale_color_manual(values = time_palette) +
  theme_classic() +
  geom_smooth(data = joint_demog |> filter(type != "practice"), method = "lm", color = "black") +
  xlab("Trial") +
  ylab("Words") +
  facet_grid(expt ~ .) +
  theme(legend.position = "none")
```

>>>>

ggplot(joint_demog, aes(x = trial + 1, y = all_words, color = type)) +
  geom_jitter(alpha = .5, color = "grey") +
  stat_summary(fun.data = "mean_cl_boot") +
  scale_x_continuous(breaks = seq(1, 20, 1), expand = c(0, 0)) +
  scale_color_manual(values = time_palette) +
  theme_classic() +
  geom_smooth(data = joint_demog |> filter(type != "practice"), method = "lm", color = "black") +
  xlab("Trial") +
  ylab("Words") +
  facet_grid(expt ~ .) +
  theme(legend.position = "none")
```
# Successful descriptions

```{r}
transcript_1 <- read_csv(here(data_loc_1, "transcripts.csv")) |>
  left_join(read_csv(here(data_loc_1, "link_transcripts.csv"))) |>
  mutate(expt = "1") |> mutate(trial=trial-2)

transcript_2 <- read_csv(here(data_loc_2, "transcripts.csv")) |>
  left_join(read_csv(here(data_loc_2, "link_transcripts.csv"))) |>
  mutate(expt = "2") |> mutate(trial=trial-4)

transcript_3 <- read_csv(here(data_loc_3, "transcripts.csv")) |>
  left_join(read_tsv(here(data_loc_3, "link_transcripts.csv"))) |>
  mutate(expt = "3") |> mutate(trial=trial-4)

transcripts <- transcript_1 |>
  bind_rows(transcript_2) |>
  bind_rows(transcript_3) |> filter(role=="S") |> filter(!is.na(description)) |> 
  group_by(trial, speaker, expt, game) |> summarize(description=str_c(description, sep=", ", collapse=", "))

joint_demog |> filter(correct==1) |> left_join(transcripts) |> select(target, expt, game, speaker, trial, description) |> View()
```
